### 2019-03-20 rebuttal.txt

We thank reviewers for their time and comments.

REV2 [rare label performance when standard RNN is inverse label order]: Intuitively we believe that predicting rare/difficult labels first is harder, and also that making mistakes early in the sequence is more damaging to performance overall. A main point of our model is that rare/difficult labels are easier to predict when other popular/easy labels are already predicted, and thus offer context. In any case, our method performs better on rare labels (Guardian label F1 = 0.292) than inverse RNN (Guardian label F1 = 0.251).

REV2 [training cost] : The reviewer is correct in that our method takes more time than vanilla-RNN, in fact by a factor of 1.5*K. "K" because there are K permutations for each datapoint, and 1.5 (approximatively) because each epoch requires one more forward pass. However, the comparisons done in the paper against state of the art RNN, are fair on performance and run time: the baselines also use K* more permutations per datapoint, so compare to these our methosd is only 1.5 (or so) slower.

REV2 [the influence of randomness/sampling in RNN model]: only Vinyals-RNN-sample has a sampling step. Other RNN models don't have any randomness. Beam search is actually deterministoic, so there is actually very little randomness involved.

REV2 [performance for frequent labels}:  We did not observe a significant improvement on frequent labels, but that is as expected. In practice, the frequent labels can be predicted pretty much with a binary relevant model that ignores dependencies, it is the rare ones that are hard. We did observe a correlation between performance gap and the frequency: the lower the frequency, the bigger the improvement.

REV2 [search over all possible combinations of label permutations]: Correct, and actually how it works: when the permutations are fewer than K, the beam search becomes exhaustive search (both training and testing). We'll make this more clear.

REV3 [applied only sequential data]: There is no sequential purpose here, in fact our contribution is to make sequence models work for sets (that is sets without a particular order)

REV3 [technical improvements are small]: we proposed a well-grounded refined objective for sets (eq 5), a beam search designed for sets, and the engineering to make it work on multilabel-data.

REV3 [don't understand Algorithma 1,3 – RNN_beam_search]: We agree that it can be clarified. But beam search definitely is happening. 
It is not that each sequence is grown independently. Instead here what is happening in Algorithm 1 inside main while loop (line 2):
- We have with K input sequences grown to size a ceratin size 
- we generate for each sequence without STOP L candidates of grown-by-1 sequences. So we have now up to K*L candidates 
- pick the best K of them for the next round.
We modify standard beam search to not repeat labels (line 6)

REV3 [not defined x in 'Mapping Sequence to Sets' section"]: "x" is defined in the introduction twice as "a document" or "instance"", and in the Algorithm 1, common in machine learning literature

REV3 [how to came up with our objective?"] : objective is explained both conceptually and mathematically in section "Adapting RNN Sequence Prediction Model to
Multi-label Set Prediction", subsection "Training by Maximizing Set Probability", and equation (5). We think the derivation of sets objective from sequences is an imprtnat contribution

REV3 [Acknowledge rebuttal = YES] Thats impossible, as our rebuttal was not written at that time.

### 2019-03-22 Introduction.tex
Updates from Overleaf

% A key research question in multi-label text classification is how to model and leverage the dependencies among labels.
Naively, one could predict each label independently without considering label dependencies. This approach is called Binary Relevance \cite{DBLP:journals/pr/BoutellLSB04,tsoumakas2007multi}, and is widely used  due to its simplicity, but it often does not deliver good performance.  Intuitively, knowing some labels---such as \texttt{sport} and \texttt{football}---should make it easier to predict \texttt{2018 world cup} and then \texttt{Russia}.  There are several methods that try to capture label dependencies by building a joint probability estimation over all labels  $p(\mathbf{y}=(y_1,y_2,...,y_L)|x)$ \cite{read2009classifier,li2016conditional,ghamrawi2005collective}. 
% \kechen{put BR before the introduction of dependency? because there is nothing about dependency by using BR} 
The most popular approach, Probabilistic Classifier Chain (PCC) \cite{read2009classifier} learns and predicts labels one-by-one in a predefined fixed order: for each label, it uses one classifier to estimate the probability of that label given all previous labels predictions, $p(y_l|y_1,...,y_{l-1},x)$. PCC's well known drawback is that errors in early predictions tend to propagate to subsequent predictions, and can become massive when the total number of label candidates $L$ is large.
% since PCC has to make a decision regarding each label candidate.

@@

% The input documents can be treated either as a sequence of words or a bag of words, and these words are represented by dense vectors.
% Attention mechanism proposed by \newcite{DBLP:journals/corr/BahdanauCB14}, at each timestamp, selects important words associated with the prediction, and assign them high attention weights. After applying attention mechanism to the word representations, we can find corresponding words that are most related to the classification task and use them to predict the labels later.

% Formally, feature words extracted by attention mechanism is called $f$, and are concatenated with hidden memory $h$ maintained by the RNN. The output vector will be passed through a nonlinearity $\phi$ before being sent to the output dense layer, and then output the probability attached with each label candidate. By multiplying over the probability of output label at each timestamp $t$, the probability of the predicted label sequence can be represented as follows:

% where $[softmax()]_i$ is the $i$-th element in softmax output, and $s_t$ represents the predicted label at timestamp $t$. 
% The whole pipeline is very similar to a machine translation, the model translate the document into a sequence of labels.

@@

%The model, grounded on gated recurrent units (GRU), consists of \textit{M} hidden layers, and at the \textit{k}th layer, the hidden state $h_t$ at timestamp $t$ is derived as:

@@

%The loss function is computed by summing up cross-entropy loss at each timestamp $t$:

@@

\section{Mapping Sequences to Sets} 
In this section, we formulate how existing works map sequences to sets, by writing down their objective functions using consistent notations. To review RNN designed for sequences, let $\mathbf{s}=(s_1,s_2,...,s_T)$ be an input sequence of outcomes, in a particular order; the order is often critical to the datapoint. An RNN model defines a probability distribution over all possible output sequences given the input in the form $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)=\prod_{t=1}^T p(s_t|x,s_1,s_2,...,s_{t-1})$. To train the RNN model, one maximizes the likelihood of the ground truth sequence $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)$.

At prediction time, one seeks to find the sequence with the highest probability $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$, and this is usually implemented approximately with a beam search procedure \cite{lowerre1976harpy} (we modified into Algorithm \ref{alg:beam_combine}). The sequence history is encoded with an internal memory vector $h_t$ which is updated over time. RNN is also often equipped with the attention mechanism \cite{DBLP:journals/corr/BahdanauCB14}, which in each  timestamp $t$ puts different weights on different words (features) and effectively attends on a list of important words $f_t$. The selected words $f_t$, the RNN memory $h_t$ at timestamp $t$, and the previous label ${s_{t-1}}$ are concatenated and used to model the label probability distribution at time $t$ as $p(s_t|x,s_1,s_2,...,s_{t-1}) \sim  \softmax(\phi(f_t,h_t,s_{t-1}))$, where $\phi$ is a non-linear function, and $\softmax$ is the normalized exponential function generalizing binary logistic regression. %Other variants of RNN, such as sequence to sequence encoder-decoder structure \cite{DBLP:conf/emnlp/ChoMGBBSB14,DBLP:conf/nips/NamMKF17}, further take into account the word order in the documents. \kechen{remove last sentence?}

% \begin{algorithm}
%     \SetKwInOut{Input}{Input}
%     \SetKwInOut{Output}{Output}
%
%     % \underline{function Beam\_Search\_for\_Given\_Set} $(\mathbf{y},m)$\;
%     \Input{Instance $x$}
%     \Output{A list of top sequences and the associated probabilities}
%     Initialize $K$ empty sequences $\mathbf{s}_1$,$\mathbf{s}_2$,...,$\mathbf{s}_K$ \\
%     \While {not all $K$ sequences end with the STOP symbol}{
%         \For {each sequence $\mathbf{s}_k$}{
%         \eIf{sequence $\mathbf{s}_k$ does not end with the STOP symbol}{
%         \For {each label $\ell$ in $\mathcal{L}$}{
%         \If{sequence $\mathbf{s}_k$ does not contain $\ell$}{
%         generate new candidate sequence by combining $\mathbf{s}_k$ and $\ell$
%         }
%
%         }
%                 generate new candidate sequence by combining $\mathbf{s}_k$ and the STOP symbol\\}{
%         consider $\mathbf{s}_k$ itself as a candidate sequence
%         }
%
%
%             % $\mathbf{y}_t = \mathbf{y} - set(s_i)$ \\
%             % \For {$j=0;j<k_3;$}{
%             % \tcp{$l_j$ is the $j$-th most possible label inferred at timestamp $t$}
%             %     \If{$l_j \in \mathbf{y}_t$}{
%             %         $s_{ij} \leftarrow s_i + l_j$\\
%             %         $j++$\\
%             %     }
%             % }
%         }
%
%     Select the top $K$ sequences among all candidates with the highest probability and assign them to $\mathbf{s}_1$,$\mathbf{s}_2$,...,$\mathbf{s}_K$
%         % \tcp{Prune sequence list to }
%         % $s \leftarrow s_{ij}[:k_3]$
%     }
%     \Return{sequence list $\mathbf{s}_1$,$\mathbf{s}_2$,...,$\mathbf{s}_K$ and the associated probabilities}
%     \caption{RNN\_Beam\_Search \cite{lowerre1976harpy}}
%     \label{alg:beam}
% \end{algorithm}

@@

 To apply RNNs to multi-label problems, one has to map the given set of labels $\mathbf{y}$ to a sequence $\mathbf{s}=(s_1,s_2,...,s_T)$, on training documents. This is usually obtained by writing the label set in a globally fixed order (e.g. by label frequency), similar to PCC.
 % After mapping the ground truth set $\mathbf{y}^{(n)}$ to a sequence $\mathbf{s}^{(n)}$ with the chosen order for each training instance $(x^{(n)},\mathbf{y}^{(n)})$,
 Once mapping is done, RNN are trained with the standard maximum likelihood objective \cite{DBLP:conf/nips/NamMKF17}: 
\begin{align}
\maximize \sum_{n=1}^N \log p(\mathbf{s}^{(n)}|x^{(n)})\\
\label{eq:standard_rnn}
\end{align}
\newcite{vinyals2015order} proposes to dynamically choose during training the sequence order deemed as most probable by the current RNN model:
\begin{align}
\maximize \sum_{n=1}^N \max_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})}\log p(\mathbf{s}|x^{(n)})
\label{eq:max_obj}
%\vspace{-2ex}
\end{align}
where the $\pi(\mathbf{y}^{(n)})$ stands for all  permutations of $\mathbf{y}^{(n)}$. This eliminates the need to manually specify label order.
However, as noticed by the authors, this objective cannot be used in the early training stages: the early order choice (often random) is reinforced by this objective and can be stuck upon permanently. To address this issue, \newcite{vinyals2015order}~also proposes two smoother alternative objectives to initialize the model training:

>>>>

% A key research question in multi-label text classification is how to model and leverage the dependencies among labels.
Naively, one could predict each label independently without considering label dependencies. This approach is called Binary Relevance \cite{DBLP:journals/pr/BoutellLSB04,tsoumakas2007multi}, and is widely used  due to its simplicity, but it often does not deliver good performance.  Intuitively, knowing some labels---such as \texttt{sport} and \texttt{football}---should make it easier to predict \texttt{2018 world cup} and then \texttt{Russia}.  There are several methods that try to capture label dependencies by building a joint probability estimation over all labels  $p(\mathbf{y}=(y_1,y_2,...,y_L)|x)$ \cite{ghamrawi2005collective,read2009classifier,DBLP:conf/icml/DembczynskiCH10,li2016conditional}. 
% \kechen{put BR before the introduction of dependency? because there is nothing about dependency by using BR} 
The most popular approach, Probabilistic Classifier Chain (PCC) \cite{DBLP:conf/icml/DembczynskiCH10} learns and predicts labels one-by-one in a predefined fixed order: for each label, it uses one classifier to estimate the probability of that label given all previous labels predictions, $p(y_l|y_1,...,y_{l-1},x)$. PCC's well known drawback is that errors in early predictions tend to propagate to subsequent predictions, and can become massive when the total number of label candidates $L$ is large. \kechen{clarify PCC define set probability while RNN define sequence probability? check our email to Krzysztof}
% since PCC has to make a decision regarding each label candidate.

@@

% The input documents can be treated either as a sequence of words or a bag of words, and these words are represented by dense vectors.
% Attention mechanism proposed by \newcite{DBLP:journals/corr/BahdanauCB14}, at each timestep, selects important words associated with the prediction, and assign them high attention weights. After applying attention mechanism to the word representations, we can find corresponding words that are most related to the classification task and use them to predict the labels later.

% Formally, feature words extracted by attention mechanism is called $f$, and are concatenated with hidden memory $h$ maintained by the RNN. The output vector will be passed through a nonlinearity $\phi$ before being sent to the output dense layer, and then output the probability attached with each label candidate. By multiplying over the probability of output label at each timestep $t$, the probability of the predicted label sequence can be represented as follows:

% where $[softmax()]_i$ is the $i$-th element in softmax output, and $s_t$ represents the predicted label at timestep $t$. 
% The whole pipeline is very similar to a machine translation, the model translate the document into a sequence of labels.

@@

%The model, grounded on gated recurrent units (GRU), consists of \textit{M} hidden layers, and at the \textit{k}th layer, the hidden state $h_t$ at timestep $t$ is derived as:

@@

%The loss function is computed by summing up cross-entropy loss at each timestep $t$:

@@

\section{Mapping Sequences to Sets} 
\kechen{officialy define T, N, $x^{(n)}$} In this section, we formulate how existing works map sequences to sets, by writing down their objective functions using consistent notations. To review RNN designed for sequences, let $\mathbf{s}=(s_1,s_2,...,s_T)$ be an input sequence of outcomes, in a particular order; the order is often critical to the datapoint. An RNN model defines a probability distribution over all possible output sequences given the input in the form $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)=\prod_{t=1}^T p(s_t|x,s_1,s_2,...,s_{t-1})$. To train the RNN model, one maximizes the likelihood of the ground truth sequence $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)$.

At prediction time, one seeks to find the sequence with the highest probability $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$, and this is usually implemented approximately with a beam search procedure \cite{lowerre1976harpy} (we modified into Algorithm \ref{alg:beam_combine}). The sequence history is encoded with an internal memory vector $h_t$ which is updated over time. RNN is also often equipped with the attention mechanism \cite{DBLP:journals/corr/BahdanauCB14}, which in each  timestep $t$ puts different weights on different words (features) and effectively attends on a list of important words $f_t$. The selected words $f_t$, the RNN memory $h_t$ at timestep $t$, and the previous label ${s_{t-1}}$ are concatenated and used to model the label probability distribution at time $t$ as $p(s_t|x,s_1,s_2,...,s_{t-1}) \sim  \softmax(\phi(f_t,h_t,s_{t-1}))$, where $\phi$ is a non-linear function, and $\softmax$ is the normalized exponential function generalizing binary logistic regression. \kechen{double check attention} %Other variants of RNN, such as sequence to sequence encoder-decoder structure \cite{DBLP:conf/emnlp/ChoMGBBSB14,DBLP:conf/nips/NamMKF17}, further take into account the word order in the documents. \kechen{remove last sentence?}

% \begin{algorithm}
%     \SetKwInOut{Input}{Input}
%     \SetKwInOut{Output}{Output}
%
%     % \underline{function Beam\_Search\_for\_Given\_Set} $(\mathbf{y},m)$\;
%     \Input{Instance $x$}
%     \Output{A list of top sequences and the associated probabilities}
%     Initialize $K$ empty sequences $\mathbf{s}_1$,$\mathbf{s}_2$,...,$\mathbf{s}_K$ \\
%     \While {not all $K$ sequences end with the STOP symbol}{
%         \For {each sequence $\mathbf{s}_k$}{
%         \eIf{sequence $\mathbf{s}_k$ does not end with the STOP symbol}{
%         \For {each label $\ell$ in $\mathcal{L}$}{
%         \If{sequence $\mathbf{s}_k$ does not contain $\ell$}{
%         generate new candidate sequence by combining $\mathbf{s}_k$ and $\ell$
%         }
%
%         }
%                 generate new candidate sequence by combining $\mathbf{s}_k$ and the STOP symbol\\}{
%         consider $\mathbf{s}_k$ itself as a candidate sequence
%         }
%
%
%             % $\mathbf{y}_t = \mathbf{y} - set(s_i)$ \\
%             % \For {$j=0;j<k_3;$}{
%             % \tcp{$l_j$ is the $j$-th most possible label inferred at timestep $t$}
%             %     \If{$l_j \in \mathbf{y}_t$}{
%             %         $s_{ij} \leftarrow s_i + l_j$\\
%             %         $j++$\\
%             %     }
%             % }
%         }
%
%     Select the top $K$ sequences among all candidates with the highest probability and assign them to $\mathbf{s}_1$,$\mathbf{s}_2$,...,$\mathbf{s}_K$
%         % \tcp{Prune sequence list to }
%         % $s \leftarrow s_{ij}[:k_3]$
%     }
%     \Return{sequence list $\mathbf{s}_1$,$\mathbf{s}_2$,...,$\mathbf{s}_K$ and the associated probabilities}
%     \caption{RNN\_Beam\_Search \cite{lowerre1976harpy}}
%     \label{alg:beam}
% \end{algorithm}

@@

 To apply RNNs to multi-label problems, one has to map the given set of labels $\mathbf{y}$ to a sequence $\mathbf{s}=(s_1,s_2,...,s_T)$, on training documents. This is usually obtained by writing the label set in a globally fixed order (e.g.\ by label frequency), similar to PCC.
 % After mapping the ground truth set $\mathbf{y}^{(n)}$ to a sequence $\mathbf{s}^{(n)}$ with the chosen order for each training instance $(x^{(n)},\mathbf{y}^{(n)})$,
 Once mapping is done, RNN are trained with the standard maximum likelihood objective \cite{DBLP:conf/nips/NamMKF17}: 
\begin{align}
\maximize \sum_{n=1}^N \log p(\mathbf{s}^{(n)}|x^{(n)})\\
\label{eq:standard_rnn}
\end{align}
\newcite{vinyals2015order} proposes to dynamically choose during training the sequence order deemed as most probable by the current RNN model:
\begin{align}
\maximize \sum_{n=1}^N \max_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})}\log p(\mathbf{s}|x^{(n)})
\label{eq:max_obj}
%\vspace{-2ex}
\end{align}
where the $\pi(\mathbf{y}^{(n)})$ stands for all  permutations of $\mathbf{y}^{(n)}$. This eliminates the need to manually specify label order.
However, as noticed by the authors, this objective cannot be used in the early training stages: the early order choice (often random) is reinforced by this objective and can be stuck upon permanently. To address this issue, \newcite{vinyals2015order}~also proposes two smoother alternative objectives to initialize the model training:

### 2019-03-22 Model.tex
Updates from Overleaf

We propose a new way of adapting RNN to multi-label set prediction, which we call \emph{set-RNN}. We appreciate the RNN model structure (defines a probability distribution over all possible sequences directly) and introduce training and prediction objectives tailored for sets that take advantage of it, while making a clear distinction between the sequence probability $p(\mathbf{s}|x)$ and the set probability $p(\mathbf{y}|x)$. 
% We notice that previous work either lack an explicit definition of set probability, or use sequence probability as the set probability, or transform sequence probability into set probability in an ad hoc way. 
% We notice that while the idea of using RNN for multi-label prediction has a lot of advantages and potentials, the existing adaptations of RNN to set prediction task are not well justified and have several issues.
 % In the literature, these two are often used interchangeably.
 % A standard RNN model only defines a probability distribution over all possible sequences directly, as mentioned earlier.
  We define the set probability as the sum of sequences probabilities for all sequence permutations of the set, namely $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. Based on this formulation, an RNN also defines a probability distribution over all possible sets indirectly since $\sum_{\mathbf{y}} p(\mathbf{y}|x)=\sum_{\mathbf{y}}\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)=\sum_{\mathbf{s}} p(\mathbf{s}|x)=1$. In standard maximum likelihood training, one wishes to maximize the likelihood of given label sets, namely, $\prod_{n=1}^N p(\mathbf{y}^{(n)}|x^{(n)})=\prod_{n=1}^N \sum_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})} p(\mathbf{s}|x^{(n)})$, or equivalently, 
\begin{align}
\maximize \sum_{n=1}^N \log \sum_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})} p(\mathbf{s}|x^{(n)})
\label{eq:right_obj}
\end{align}
  % Having this clearly defined set probability is critical for our formulation as it naturally leads to our training and prediction methods.

@@

This training objective (\ref{eq:right_obj}) looks similarly to the objective (\ref{eq:wrong_obj}) considered in previous work \cite{vinyals2015order}, but in fact they correspond to very different transformations. Under the maximum likelihood framework, our objective (\ref{eq:right_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$, while objective (\ref{eq:wrong_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\prod_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. The latter transformation does not define a valid probability distribution over $\mathbf{y}$ (i.e., $\sum_{\mathbf{y}} p(\mathbf{y}|x)\neq 1$), and it has an undesired  consequence in practical model training: because of the multiplication operation, the RNN model has to assign equally high probabilities to all sequence permutations of the given label set in order to maximize the set probability. If only some sequence permutations receive high probabilities while others receive low probabilities, the set probability will still be low. In other words, if for each document, RNN finds one  good way of ordering relevant labels (such as hierarchically) and allocates most of the probability mass to the sequence in that order, the model will be penalized heavily.  As a consequence the model has little freedom in discovering and concentrating on some natural label order. In contrast, with our proposed training objective, in which the multiplication operation is replaced by the  summation operation, it suffices to find only one reasonable permutation of the labels for each document. \emph{Different documents can have different label orders}; thus our proposed training objective gives the RNN model far more freedom on label order. The other two objectives (\ref{eq:max_obj}) and (\ref{eq:sample_obj}) proposed in \cite{vinyals2015order} are less restrictive than  (\ref{eq:wrong_obj}), but they have to work in conjunction with (\ref{eq:wrong_obj}) because of the self reinforcement issue. Our proposed training objective has a natural probabilistic interpretation, does not suffer from self reinforcement issue and can serve as a stand alone training objective. 
% Another approach used in previous work, which is to pick one fixed sequence order (e.g., by label frequency) in advance, forces the model to only assign high probabilities to sequences in that order.
% , and therefore does not leave any opportunity for the model to explore label orders. Since in multi-label data, labels often do not have an obvious ordering and human heuristics are often suboptimal, it is advantageous to let the training procedure discover label orderings, on a per sample basis.
% \subsection{A Brief Review of RNN and Attention}

@@

\subsection{Training by Maximizing Set Probability}
Training an RNN model with the proposed objective (\ref{eq:right_obj}) requires summing up $|\mathbf{y}|!$  sequence probabilities for a set $\mathbf{y}$, where $|\mathbf{y}|$ is the cardinality of the set.  Thus evaluating this objective exactly can be intractable. We can approximate this sum by only considering the top $K$ high probability sequences produced by the RNN model. We introduce a variant of beam search for sets with width $K$ and with the search candidates in each step restricted to only labels in the set (see Algorithm~\ref{alg:beam_combine}). This approximate inference procedure is carried out repeatedly before each batch training step, in order to find high probability sequences for all training instances occurring in that batch. The overall training procedure is summarized in Algorithm \ref{alg:train_beam}.% \cheng{add pseudo code}

@@

    % Initialize model parameters\\
    \ForEach {epoch, batch}{
        % \ForEach {batch }{
            \ForEach{$(x^{n},\mathbf{y}^{n})$ in the batch}{
                Get top $K$ sequences :\\
		    	$\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}, p(\mathbf{s}^n_{1}|x^n),...,p(\mathbf{s}^n_{K}|x^n)\}$=  \hspace{4ex}=Beam\_Search($(x^{n},\mathbf{y}^{n}, ALL=1$)\\
                }
            Update model parameters by maximizing $\sum\limits_{(x^{n},\mathbf{y}^{n}) \in \text{batch}} \log \sum\limits_{\mathbf{s}\in\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}\}} p(\mathbf{s}|x^{n})$
        % }
    }
    \caption{Training method for set-RNN}
    \label{alg:train_beam}
\end{algorithm}

\subsection{Predicting the Most Probable Set}
The transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$ also naturally leads to a prediction procedure, which is different from the previous standard of directly using most probable sequence as a set. We instead aim to find the most likely set $\hat{\mathbf{y}}=\arg\max_{\mathbf{y}} p(\mathbf{y}|x)$, which involves summing up probabilities for all of its permutations (see Table~1). To make it tractable, we propose a two-level beam search procedure. First we run standard RNN beam search (Algorithm \ref{alg:beam_combine}) to generate a list of high probability sequences.  We then consider the label set associated with each label sequence.  For each set, we evaluate its probability using the same approximate summation procedure as the one used during model training (Algorithm~\ref{alg:beam_combine}): we run our modified beam search to find the top few high probability sequences associated with the set and sum up their probabilities. Among these sets that we have evaluated, we choose the one with the highest probability as the prediction. The overall prediction procedure is summarized in Algorithm~\ref{alg:test}. As we shall show in case study, the most probable set may not correspond to the most probable sequence; these are certainly cases where our method has an advantage.
%\textbf{Variant of beam search.} To obtain the top high probability sequences associated with a given set, beam search

>>>>

We propose a new way of adapting RNN to multi-label set prediction, which we call \emph{set-RNN}. We appreciate the RNN model structure (defines a probability distribution over all possible sequences directly) and introduce training and prediction objectives tailored for sets that take advantage of it, while making a clear distinction between the sequence probability $p(\mathbf{s}|x)$ and the set probability $p(\mathbf{y}|x)$. 
% We notice that previous work either lack an explicit definition of set probability, or use sequence probability as the set probability, or transform sequence probability into set probability in an ad hoc way. 
% We notice that while the idea of using RNN for multi-label prediction has a lot of advantages and potentials, the existing adaptations of RNN to set prediction task are not well justified and have several issues.
 % In the literature, these two are often used interchangeably.
 % A standard RNN model only defines a probability distribution over all possible sequences directly, as mentioned earlier.
  We define the set probability as the sum of sequences probabilities for all sequence permutations of the set, namely $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. Based on this formulation, an RNN also defines a probability distribution over all possible sets indirectly since $\sum_{\mathbf{y}} p(\mathbf{y}|x)=\sum_{\mathbf{y}}\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)=\sum_{\mathbf{s}} p(\mathbf{s}|x)=1$. \kechen{It's still possible for the model to predict a label twice. I'd like to see a mathematical treatment of this case in your framework. Would you treat the predicted multiset as a set by ignoring repeated entries? Would you force the probability of a multiset down to zero? The mere fact that these can be predicted by the model means that they should eat away at some of the probability mass devoted to pure sets. You need a way of handling this. } In standard maximum likelihood training, one wishes to maximize the likelihood of given label sets, namely, $\prod_{n=1}^N p(\mathbf{y}^{(n)}|x^{(n)})=\prod_{n=1}^N \sum_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})} p(\mathbf{s}|x^{(n)})$, or equivalently, 
\begin{align}
\maximize \sum_{n=1}^N \log \sum_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})} p(\mathbf{s}|x^{(n)})
\label{eq:right_obj}
\end{align}
  % Having this clearly defined set probability is critical for our formulation as it naturally leads to our training and prediction methods.

@@

This training objective (\ref{eq:right_obj}) looks similar to the objective (\ref{eq:wrong_obj}) considered in previous work \cite{vinyals2015order}, but in fact they correspond to very different transformations. Under the maximum likelihood framework, our objective (\ref{eq:right_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$, while objective (\ref{eq:wrong_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\prod_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. The latter transformation does not define a valid probability distribution over $\mathbf{y}$ (i.e., $\sum_{\mathbf{y}} p(\mathbf{y}|x)\neq 1$), and it has an undesired  consequence in practical model training: because of the multiplication operation, the RNN model has to assign equally high probabilities to all sequence permutations of the given label set in order to maximize the set probability. \kechen{You can actually be more specific about the flaw in Eq. 3. Using Jensen’s inequality, you can show that the total probability mass in Eq. 3 will be less than or equal to the true amount of probability mass (1). In this sense, your predecessors are optimizing a *bound* on the log-likelihood, while you optimize it directly.} If only some sequence permutations receive high probabilities while others receive low probabilities, the set probability will still be low. In other words, if for each document, RNN finds one  good way of ordering relevant labels (such as hierarchically) and allocates most of the probability mass to the sequence in that order, the model will be penalized heavily.  As a consequence the model has little freedom in discovering and concentrating on some natural label order. In contrast, with our proposed training objective, in which the multiplication operation is replaced by the  summation operation, it suffices to find only one reasonable permutation of the labels for each document. \emph{Different documents can have different label orders}; thus our proposed training objective gives the RNN model far more freedom on label order. The other two objectives (\ref{eq:max_obj}) and (\ref{eq:sample_obj}) proposed in \cite{vinyals2015order} are less restrictive than  (\ref{eq:wrong_obj}), but they have to work in conjunction with (\ref{eq:wrong_obj}) because of the self reinforcement issue. Our proposed training objective has a natural probabilistic interpretation, does not suffer from self reinforcement issue and can serve as a stand alone training objective. 
% Another approach used in previous work, which is to pick one fixed sequence order (e.g., by label frequency) in advance, forces the model to only assign high probabilities to sequences in that order.
% , and therefore does not leave any opportunity for the model to explore label orders. Since in multi-label data, labels often do not have an obvious ordering and human heuristics are often suboptimal, it is advantageous to let the training procedure discover label orderings, on a per sample basis.
% \subsection{A Brief Review of RNN and Attention}

@@

\subsection{Training by Maximizing Set Probability}
Training an RNN model with the proposed objective (\ref{eq:right_obj}) requires summing up $|\mathbf{y}|!$  sequence probabilities for a set $\mathbf{y}$, where $|\mathbf{y}|$ is the cardinality of the set.\blue{permutation}  Thus evaluating this objective exactly can be intractable. We can approximate this sum by only considering the top $K$ high probability sequences produced by the RNN model. We introduce a variant of beam search for sets with width $K$ and with the search candidates in each step restricted to only labels in the set (see Algorithm~\ref{alg:beam_combine}). This approximate inference procedure is carried out repeatedly before each batch training step, in order to find high probability sequences for all training instances occurring in that batch. The overall training procedure is summarized in Algorithm \ref{alg:train_beam}.% \cheng{add pseudo code}

@@

    % Initialize model parameters\\
    \ForEach {batch}{
        % \ForEach {batch }{
            \ForEach{$(x^{n},\mathbf{y}^{n})$ in the batch}{
                Get top $K$ sequences :\\
		    	$\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}, p(\mathbf{s}^n_{1}|x^n),...,p(\mathbf{s}^n_{K}|x^n)\}$=  \hspace{4ex}=Beam\_Search($(x^{n},\mathbf{y}^{n}, ALL=1$)\\
                }
            Update model parameters by maximizing $\sum\limits_{(x^{n},\mathbf{y}^{n}) \in \text{batch}} \log \sum\limits_{\mathbf{s}\in\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}\}} p(\mathbf{s}|x^{n})$
        % }
    }
    \caption{Training method for set-RNN}
    \label{alg:train_beam}
\end{algorithm}

\subsection{Predicting the Most Probable Set}
The transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$ also naturally leads to a prediction procedure, which is different from the previous standard of directly using most probable sequence as a set. We instead aim to find the most likely set $\hat{\mathbf{y}}=\arg\max_{\mathbf{y}} p(\mathbf{y}|x)$, which involves summing up probabilities for all of its permutations (see Table~1).\blue{permutation} To make it tractable, we propose a two-level beam search procedure. First we run standard RNN beam search (Algorithm \ref{alg:beam_combine}) to generate a list of high probability sequences.  We then consider the label set associated with each label sequence.  For each set, we evaluate its probability using the same approximate summation procedure as the one used during model training (Algorithm~\ref{alg:beam_combine}): we run our modified beam search to find the top few high probability sequences associated with the set and sum up their probabilities. Among these sets that we have evaluated, we choose the one with the highest probability as the prediction. The overall prediction procedure is summarized in Algorithm~\ref{alg:test}. As we shall show in case study, the most probable set may not correspond to the most probable sequence; these are certainly cases where our method has an advantage.
%\textbf{Variant of beam search.} To obtain the top high probability sequences associated with a given set, beam search
